Topic Scores

### 2019-03-13 Topic Scores.Rmd

---
title: "Topic Scores"
author: "DARS"
date: "2/18/2019"
output: pdf_document
---
#Set up
##Libraries
```{r libraries}
library(tidyverse)
```

##Raw Data
```{r setup, include=FALSE}
#
##Import d_course and d_transcript
load("Output/data_general.RDATA")
load("Output/data_pillar_1.RDATA")

#
##Import LDA_models
load("Output/topic_model.RDATA")

rm(lists, d_AoD, d_assessment, d_ILO)
```

##Models in list:
```{r models in list}
LDA_models <- list()
LDA_models$description <- LDA_description_35
LDA_models$overview <- LDA_overview_35
LDA_models$manual <- LDA_manual_40

rm(LDA_description_35, LDA_overview_35, LDA_manual_40)
```

## Getting Functions (gamma and beta) 
```{r getting functions}
get_beta <- function(results){

@@

##Getting applied (gamma and beta) 
```{r getting beta and gamma}
distribution <- list()

@@

##Inspect topics
```{r inspect topics}
inspect_topics <- function(d_beta = distribution$beta){
  d_beta %>%
    group_by(topic) %>%
    top_n(10, beta)

@@

#
##View
#View(topics$manual)

##Selectig keywords
```{r}
get_top_words <- function(d_beta, n = 3){
  d_beta %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

>>>>

---
title: "Topic Scores"
author: "DARS"
date: "2/18/2019"
output: pdf_document
---
#Set up
##Libraries
```{r libraries}
library(tidyverse) #already in Pillar2
```

##Raw Data
```{r setup1, include=FALSE}
#
##Import d_course and d_transcript
load("Output/data_pillar_1.RDATA") #check if included in pillar 2
```

```{r setup2, include = FALSE}
#
##Import LDA_models
start.time <- Sys.time()
load("Output/topic_model_gb.RDATA") #this takes a long time, won't be needed in pillar 2
end.time <- Sys.time()
print(start.time-end.time)
```

Cropping model and getting distributions:
```{r}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

#Crop models
TM_overview <- topic_model_gb %>%
  filter(n_topic== n_topics_overview)

TM_manual   <- topic_model_gb %>%
  filter(n_topic== n_topics_manual)

#Distributions
distribution <- list()

distribution$beta$overview  <- TM_overview %>% pull(b_overview)
distribution$beta$manual    <- TM_manual   %>% pull(b_manual)

distribution$gamma$overview <- TM_overview %>% pull(g_overview)
distribution$gamma$manual   <- TM_manual   %>% pull(g_manual)

##Models in list:
```{r models in list, eval = FALSE}
LDA_models <- list()
#LDA_models$description <- LDA_description_35 #this is the old code

LDA_models$overview <- topic_model %>% 
  filter (n_topic == 36) %>%
  pull(TM_overview)

LDA_models$manual <- topic_model %>% 
  filter (n_topic == 40) %>%
  pull(TM_manual)

#rm(topic_model)
```

## Getting Functions (gamma and beta) this is silenced because we clean before importing
```{r getting functions, eval = FALSE}
get_beta <- function(results){

@@

##Getting applied (gamma and beta) 
```{r getting beta and gamma, eval = FALSE}
distribution <- list()

@@

##Inspect topics
THE TOPICS ARE SUPPER STRANGE!
```{r inspect topics}

inspect_topics <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta)

@@

#
##View
#View(topics$manual)
```

##Selectig keywords
```{r}
get_top_words <- function(d_beta, n = 3){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}
